---
title: "Twitter and Physical Activity"
output:
  github_document: default
  html_notebook: default
---
```{r message=FALSE}
library(tidyverse)
library(betareg)
library(fitdistrplus)
library(Hmisc)
library(knitr)
library(lmtest)
```

The compiled dataset contains a subset of US counties (names and FIPS codes).

The associated data for each county is as follows:

* All_Tweets: the total collected number of tweets from that county
* PA_Tweets: the number of tweets identified as physical activity-related
* Inactivity_Cases: TODO
* Inactivity_Percent: TODO
* Inactivity_Percent_AgeAdjusted: TODO
* Gini_Index: TODO
* Gini_Index_MoE: the margin of error of the Gini index estimate

```{r results='asis'}
# This helper will render legible tables in both RStudio and the generated markdown.
display <- function(x) {
  if (interactive()) (x)
  else kable(x)
}

all_data <- read.csv("data/all_data.csv")
cat('Rows in complete dataset: ', nrow(all_data))
display(head(all_data))
```

Not all counties in the dataset have tweet or physical activity data available, so we must filter those out.

```{r}
# Remove rows with missing values
cleaned_data <- na.omit(all_data)
cleaned_data <- cleaned_data[cleaned_data$Tweets.All >= cleaned_data$Tweets.PA,]
display(all_data[rowSums(is.na(all_data)) > 0,])
cat('Rows after cleaning: ', nrow(cleaned_data))
```

We must also normalize the percentages (expressed here as a number /100) to values we can use for a beta distribution (i.e. 0-1)
```{r}
cleaned_data$Tweets.PA.Percent <- cleaned_data$Tweets.PA / cleaned_data$Tweets.All
cleaned_data$Inactivity.Percent <- cleaned_data$Inactivity.Percent / 100
cleaned_data$Inactivity.Ageadjusted <- cleaned_data$Inactivity.Ageadjusted / 100

display(head(arrange(cleaned_data, desc(Tweets.All))))
display(head(arrange(cleaned_data, desc(Tweets.PA))))

vars <- setdiff(names(cleaned_data), c("FIPS", "State", "County"))
display(as.data.frame(do.call(cbind, lapply(cleaned_data[vars], summary))))
```

The count data are heavily right-skewed with notable outliers. This is partly attributable to the disparity in population between counties
(e.g. LA, the most populous county, has a similar relative magnitude of tweets)

```{r fig.width=20, fig.height=15}
par(mfrow=c(ceiling(length(vars) / 2), 2))
for (v in vars) {
  boxplot(cleaned_data[v], main = v, horizontal = TRUE)
}
```

```{r fig.width=20, fig.height=15}
par(mfrow=c(2, 2))
hist(cleaned_data$Inactivity.Percent)
descdist(cleaned_data$Inactivity.Percent)

hist(cleaned_data$Inactivity.Ageadjusted)
descdist(cleaned_data$Inactivity.Ageadjusted)

fit.beta1 <- fitdist(cleaned_data$Inactivity.Percent, "beta")
plot(fit.beta1)

fit.beta2 <- fitdist(cleaned_data$Inactivity.Ageadjusted, "beta")
plot(fit.beta2)
```

Correlation of variables:

```{r out.width=20}
results <- rcorr(as.matrix(cleaned_data[vars]), type = "pearson")
display(as.data.frame(results$r))
display(as.data.frame(results$P))
```

Correlation of variables:

```{r out.width=20}
results <- rcorr(as.matrix(cleaned_data[vars]), type = "spearman")
display(as.data.frame(results$r))
display(as.data.frame(results$P))
```

Comparing models:

```{r}
m1 <- betareg(Inactivity.Percent ~ Tweets.PA, data = cleaned_data)
summary(m1)

m2 <- update(m1, . ~ . + Gini_Index.Estimate)
summary(m2)

m3 <- update(m2, . ~ . + Education.College.Estimate)
summary(m3)

m4 <- update(m3, . ~ . + Tweets.PA.Positive - Tweets.PA)
summary(m4)

m5 <- update(m3, . ~ . + Tweets.PA.Negative - Tweets.PA)
summary(m5)

m6 <- update(m3, . ~ . + Tweets.PA.Positive + Tweets.PA.Negative + Tweets.PA.Neutral - Tweets.PA)
summary(m6)

compareModels <- function(...) {
  res = AIC(...)
  rownames(res) <- paste('m', 1:nrow(res), sep = '')
  res$BIC <- BIC(...)$BIC
  display(res)
}
compareModels(m1, m2, m3, m4, m5, m6)
```

```{r}
m1.aa <- betareg(Inactivity.Ageadjusted ~ Tweets.PA, data = cleaned_data)
summary(m1.aa)

m2.aa <- update(m1.aa, . ~ . + Gini_Index.Estimate)
summary(m2.aa)

m3.aa <- update(m2.aa, . ~ . + Education.College.Estimate)
summary(m3.aa)

m4.aa <- update(m3.aa, . ~ . + Tweets.PA.Positive - Tweets.PA)
summary(m4.aa)

m5.aa <- update(m3.aa, . ~ . + Tweets.PA.Negative - Tweets.PA)
summary(m5.aa)

m6.aa <- update(m3.aa, . ~ . + Tweets.PA.Positive + Tweets.PA.Negative + Tweets.PA.Neutral - Tweets.PA)
summary(m6.aa)

compareModels(m1.aa, m2.aa, m3.aa, m4.aa, m5.aa, m6.aa)
```

```{r fig.width=20, fig.height=15}
par(mfrow=c(2, 1))
scatter.smooth(cleaned_data$Tweets.PA, cleaned_data$Inactivity.Percent)
scatter.smooth(log1p(cleaned_data$Tweets.PA), cleaned_data$Inactivity.Percent)
```

```{r fig.width=20, fig.height=10}
m.test <- m3
lrtest(m.test)
# gleverage(m4.aa)
m.test.rmse <- sqrt(mean(m.test$residuals^2))
print(m.test.rmse)
plot(m.test)
```
```{r}
library(classInt)
intervals <- classIntervals(cleaned_data$Inactivity.Ageadjusted, n = 5, style = 'jenks')
```


```{r fig1, fig.width=12, fig.height=7}
library(scales)
library(usmap)
library(viridis)

cleaned_data$quants <-  cut(cleaned_data$Inactivity.Ageadjusted, intervals$brks, include.lowest = T)

cleaned_data$predicted <- predict(m3, type = 'response')
cleaned_data$pred_quants <-  cut(cleaned_data$predicted, intervals$brks, include.lowest = T)

counties_map <- us_map(regions = 'counties')
counties_map$fips <- as.numeric(counties_map$fips)
plot_data <- inner_join(counties_map, cleaned_data, by = c('fips'= 'FIPS'))

states <- us_map(region = 'states')

scale_dir <- 1
ggplot(plot_data, aes(long, lat, group = group)) + 
  geom_polygon(aes(fill = Inactivity.Ageadjusted), colour = alpha('white', 1 / 2), size = 0.2) +
  geom_polygon(data = states, colour = 'white', fill = NA) +
  coord_equal() +
  theme_minimal() +
  theme(axis.line = element_blank(), axis.text = element_blank(),
        axis.ticks = element_blank(), axis.title = element_blank(),
        legend.position = 'bottom') +
  scale_fill_distiller(
    #option = 'magma',
    direction = scale_dir,
    labels = percent,
                     guide = guide_colourbar(
                       direction = 'horizontal',
                       title = 'Age-adjusted physical inactivity level',
                       title.position = 'top',
                       title.hjust = .5,
                       barheight = unit(3, units = 'mm'),
                       barwidth = unit(100, units = 'mm')
                     ))

ggplot(plot_data, aes(long, lat, group = group)) + 
  geom_polygon(aes(fill = Tweets.PA.Percent), colour = alpha('white', 1 / 2), size = 0.2) +
  geom_polygon(data = states, colour = 'white', fill = NA) +
  coord_equal() +
  theme_minimal() +
  theme(axis.line = element_blank(), axis.text = element_blank(),
        axis.ticks = element_blank(), axis.title = element_blank(),
        legend.position = 'bottom') +
  scale_fill_distiller(
    #option = 'magma',
    direction = -scale_dir,
    labels = percent,
    trans = 'sqrt',
                     guide = guide_colourbar(
                       direction = 'horizontal',
                       title = 'Percentage of physical activity related tweets',
                       title.position = 'top',
                       title.hjust = .5,
                       barheight = unit(3, units = 'mm'),
                       barwidth = unit(100, units = 'mm')
                     ))


ggplot(plot_data, aes(long, lat, group = group)) + 
  geom_polygon(aes(fill = Gini_Index.Estimate), colour = alpha('white', 1 / 2), size = 0.2) +
  geom_polygon(data = states, colour = 'white', fill = NA) +
  coord_equal() +
  theme_minimal() +
  theme(axis.line = element_blank(), axis.text = element_blank(),
        axis.ticks = element_blank(), axis.title = element_blank(),
        legend.position = 'bottom') +
  scale_fill_distiller(
      #option = 'magma',
    direction = scale_dir,
      guide = guide_colourbar(
        direction = 'horizontal',
        title = 'Gini Index of income inequality',
        title.position = 'top',
        title.hjust = .5,
        barheight = unit(3, units = 'mm'),
        barwidth = unit(100, units = 'mm')
      ))

ggplot(plot_data, aes(long, lat, group = group)) + 
  geom_polygon(aes(fill = Education.College.Estimate / 100), colour = alpha('white', 1 / 2), size = 0.2) +
  geom_polygon(data = states, colour = 'white', fill = NA) +
  coord_equal() +
  theme_minimal() +
  theme(axis.line = element_blank(), axis.text = element_blank(),
        axis.ticks = element_blank(), axis.title = element_blank(),
        legend.position = 'bottom') +
  scale_fill_distiller(
    #option = 'magma',
    labels = percent,
    direction = scale_dir,
                     guide = guide_colourbar(
                       direction = 'horizontal',
                       title = 'Percentage of college educated population',
                       title.position = 'top',
                       title.hjust = .5,
                       barheight = unit(3, units = 'mm'),
                       barwidth = unit(100, units = 'mm')
                     ))

ggplot(plot_data, aes(long, lat, group = group)) + 
  geom_polygon(aes(fill = quants), colour = alpha('white', 1 / 2), size = 0.2) +
  geom_polygon(data = states, colour = 'white', fill = NA) +
  coord_equal() +
  theme_minimal() +
  theme(axis.line = element_blank(), axis.text = element_blank(),
        axis.ticks = element_blank(), axis.title = element_blank(),
        #legend.position = 'bottom',
        plot.background = element_rect(fill = "#f5f5f2", color = NA), 
        panel.background = element_rect(fill = "#f5f5f2", color = NA), 
        legend.background = element_rect(fill = "#f5f5f2", color = NA),
        panel.border = element_blank()
        ) +
  scale_fill_viridis(
    option = 'magma',
    name = 'Age-adjusted physical inactivity',
    discrete = T,
    alpha = .80
  )
ggplot(plot_data, aes(long, lat, group = group)) + 
  geom_polygon(aes(fill = pred_quants), colour = alpha('white', 1 / 2), size = 0.2) +
  geom_polygon(data = states, colour = 'white', fill = NA) +
  coord_equal() +
  theme_minimal() +
  theme(axis.line = element_blank(), axis.text = element_blank(),
        axis.ticks = element_blank(), axis.title = element_blank(),
        #legend.position = 'bottom',
        plot.background = element_rect(fill = "#f5f5f2", color = NA), 
        panel.background = element_rect(fill = "#f5f5f2", color = NA), 
        legend.background = element_rect(fill = "#f5f5f2", color = NA),
        panel.border = element_blank()
        ) +
  scale_fill_viridis(
    option = 'magma',
    name = 'Age-adjusted physical inactivity',
    discrete = T,
    alpha = .80
  )
```